---
title: "R Notebook"
output: html_notebook
---

 

```{r}
# Import data
df_raw = read.csv("Data/CaseStudy2-data.csv", header=TRUE, stringsAsFactors = TRUE)
head(df_raw)
```
# Exploratory Data Analysis 


## Monthly Income & Attrition
```{r}
# MonthlyIncome
ggplot(df, aes(x=Attrition, y=MonthlyIncome, color=Attrition, fill= Attrition)) +
  geom_boxplot( color = "black")+
  labs(title="Monthly Income vs. Attrition",x="Attrition", y = "Monthly Income $")+ scale_fill_few(palette = 'Dark')+ theme_few()
```
## Job Involvement & Attrition 
```{r}
library(ggthemes)
df %>% ggplot(aes(x = JobInvolvement, fill = Attrition)) +
  geom_bar(position = 'fill', color="black") +
  coord_flip() + 
  scale_fill_few(palette = 'Dark')+ theme_few() +ggtitle("Job Involvement & Attrition")
```

### Job Involvement & Attrition based on OverTime
```{r}
df %>% ggplot(aes(x = JobInvolvement, fill = Attrition)) +
  geom_bar(position = 'fill', color="black") +
  coord_flip() +
  facet_wrap( ~ OverTime) + 
  scale_fill_few(palette = 'Dark') + 
  theme_few() + ggtitle("Job Involvement & Attrition based on OverTime")
```
## Work-Life Balance & Attrition 
```{r}
df %>% ggplot(aes(x = WorkLifeBalance, fill = Attrition)) +
  geom_bar(position = 'fill', color="black") +
  coord_flip() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few() + ggtitle("Work-Life Balance & Attrition")
```
### Work-Life Balance & Attrition based on JobRole
```{r}
df %>% ggplot(aes(x = WorkLifeBalance, fill = Attrition)) +
  geom_bar(position = 'fill', color="black") +
  coord_flip() +
  facet_wrap( ~ JobRole) + 
  scale_fill_few(palette = 'Dark') + 
  theme_few() +ggtitle("Work-Life Balance & Attrition based on JobRole")
```
### Work-Life Balance & Attrition based on JobLevel 
```{r}
df %>% ggplot(aes(x = WorkLifeBalance, fill = Attrition)) +
  geom_bar(position = 'fill', color="black") +
  coord_flip() +
  facet_wrap( ~ JobLevel) + 
  scale_fill_few(palette = 'Dark') + 
  theme_few() +ggtitle("Work-Life Balance & Attrition based on JobLevel")
```
### Work-Life Balance & Attrition based on OverTime
```{r}
df %>% ggplot(aes(x = WorkLifeBalance, fill = Attrition)) +
  geom_bar(position = 'fill', color="black") +
  coord_flip() +
  facet_wrap( ~ OverTime) + 
  scale_fill_few(palette = 'Dark') + 
  theme_few() +ggtitle("Work-Life Balance & Attrition based on OverTime")
```
## OverTime & Attrition 
```{r}
df %>% ggplot(aes(x = OverTime, fill = Attrition)) +
  geom_bar(position = 'fill') +
  coord_flip() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()
```
### OverTime & Attrition based on Job Role
```{r}
df %>% ggplot(aes(x = OverTime, fill = Attrition)) +
  geom_bar(position = 'fill') +
  coord_flip() +
  facet_wrap( ~ JobRole) + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()
```
### OverTime & Attrition based on Job Level
```{r}
df %>% ggplot(aes(x = OverTime, fill = Attrition)) +
  geom_bar(position = 'fill') +
  coord_flip() +
  facet_wrap( ~ JobLevel) + 
  scale_fill_few(palette = 'Dark') + 
  theme_few()

```
### OverTime & Attrition based on MonthlyIncome
```{r}
train %>% 
  ggplot(aes(x = Attrition,
             y = MonthlyIncome,
             fill = Attrition)) +
  geom_boxplot() + 
  facet_wrap(~ OverTime) +
  scale_fill_few(palette = 'Dark') + 
  theme_few() +
  ggtitle('MonthlyIncome by Attrition and Overtime')
```








