---
title: "Case Study 2"
output: html_notebook
---

# Introduction

## Data 

*Dataset:* CaseStudy2-data.csv

*Columns Reference* 
1. ID 
2. Age
3. Attrition 
4. Business Travel 
5. DailyRate
6. Department 
7. DistanceFromHome
8. Education 
9. EducationField
10. EmployeeCount
11. EmployeeNumber
12. EnvironmentSatisfaction
13. Gender
14. HourlyRate

# Preliminary Data Collection & Cleaning

## Packages 
```{r}
library(tidyverse)
library(dplyr)
library(scales)
library(ggplot2)
library(inspectdf)
library(kableExtra)
library(DataExplorer)
library(plyr)
library(caret)
library(e1071)
library(ggthemes)
```

## Load Data
```{r}
# Import data
df_raw = read.csv("Data/CaseStudy2-data.csv", header=TRUE, stringsAsFactors = TRUE)
head(df_raw)

# Validation data set with No Attrition 
df_attr = read.csv("Data/CaseStudy2CompSet_No_Attrition.csv", header=TRUE, stringsAsFactors=TRUE)
head(df_attr)

# Validation data set with No Salary 
df_salary = read.csv("Data/CaseStudy2CompSet_No_Salary.csv", header=TRUE, stringsAsFactors=TRUE)
head(df_salary)

dfAll = rbind.fill(df_raw, df_attr)
dfAll = rbind.fill(dfAll, df_salary)
head(dfAll)

nrow(dfAll)
```

## Clean Data Set 

### Missing data & Duplicates

No missing values or duplicates in the data
```{r}
colSums(is.na(df_raw))
df_raw[duplicated(df_raw),]

```
### Unique values for categorical variables
```{r}

df_raw %>% select_if(is.factor) %>%
  summarise_all(~n_distinct(.)) %>% 
  pivot_longer(., everything(), names_to = "columns", values_to = "count_unique_values") %>%
  arrange(desc(count_unique_values))
```
Over 18 column only has 1 unique value therefore can be elimated from the data set

```{r}
str(df_raw)
```
### Remove Unnecessary Rows 
- Over18, EmployeeCount, StandardHours all are constant so can be removed + remove EmployeeNumber & ID as they are purely for identification
- Add AgeGroup column with different levels 
- Create new column for AttritionCode with 0 and 1 factor levels (0=No, 1=Yes)

Explore Structure of Data Set
```{r}
names(df_raw) # variable names 
dim(df_raw) # data set dimensions
str(df_raw) # data set structure
summary(df_raw) # data set summary
```

```{r}
dim(df_raw[df_raw$Over18 == "N",])
dim(df_raw[df_raw$EmployeeCount != 1,])
dim(df_raw[df_raw$StandardHours != 80,])

# Create age groups 
df$AgeGroup <- ""
df[df$Age < 20, ]$AgeGroup <- "<20"
df[df$Age >= 20 & df$Age < 30, ]$AgeGroup <- "20-29"
df[df$Age >= 30 & df$Age < 40, ]$AgeGroup <- "30-39"
df[df$Age >= 40 & df$Age < 50, ]$AgeGroup <- "40-49"
df[df$Age >= 50 & df$Age < 60, ]$AgeGroup <- "50-59"
df[df$Age >= 60, ]$AgeGroup <- "60+"
df$AgeGroup <- factor(df$AgeGroup, level = c("<20", "20-29", "30-39", "40-49", "50-59", "60+"))


head(df)

# remove unnecessary columns
df = subset(df_raw, select= -c(Over18,EmployeeCount,StandardHours, ID, EmployeeNumber) )
glimpse(df)



```

## Inspect Categorical Levels
```{r}
library(inspectdf)
inspect_cat(df)
head(df_cat)
df_cat$levels
```

## Create DataFrame with factors as numeric (for knn)
```{r}
df_num = df

# BusinessTravel into (0-Non-Travel,1-Travel_Rarely,2-Travel_Frequently)
df_num$BusinessTravel <- as.numeric(factor(df_num$BusinessTravel,
                                                        levels = c("Travel_Frequently", "Travel_Rarely", "Non-Travel"),
                                                        labels = c(2,1,0), ordered = TRUE))

# Department into (0-Research&Development, 1-Sales, 2-Human Resources)
df_num$Department <- as.numeric(factor(df_num$Department,
                                                        levels = c("Research & Development", "Sales", "Human Resources"),
                                                        labels = c(0,1,2), ordered = TRUE))

# Education Field into (0-Life Sciences, 1-Medical, 2-Marketing, 3-Technical Degree, 4-Human Resources, 5-Other)
df_num$EducationField <- as.numeric(factor(df_num$EducationField,
                                                        levels = c("Life Sciences", "Medical", "Marketing", "Technical Degree", "Human Resources", "Other"),
                                                        labels = c(0,1,2,3,4,5), ordered = TRUE))

# Job Role into (0-Sales Executive, 1-Research Scientist, 2-Laboratory Technician, 3-Manufacturing Director, 4-Healthcare Representative, 5-Sales Representative, 6-Manager, 7-Research Director, 8-Human Resources) 
df_num$JobRole <- as.numeric(factor(df_num$JobRole,
                                                        levels = c("Sales Executive", "Research Scientist", "Laboratory Technician", "Manufacturing Director", "Healthcare Representative", "SalesRepresentative", "Manager", "Research Director", "Human Resources"),
                                                        labels = c(0,1,2, 3, 4, 5, 6, 7, 8), ordered = TRUE))

# MaritalStatus into (0-Divorced,1-Single,2-Married)
df_num$MaritalStatus <- as.numeric(factor(df_num$MaritalStatus,
                                                        levels = c("Married", "Single", "Divorced"),
                                                        labels = c(2,1,0), ordered = TRUE))


# create new column for Attrition factor levels
#0 = No, 1 = Yes
df_num$Attrition <- mapvalues(df_num$Attrition, from=c('Yes', 'No'), to = c(1,0))
df_num$Attrition=as.numeric(df_num$Attrition)

df_num$Gender <- mapvalues(df_num$Gender, from=c('Male', 'Female'), to = c(1,0))
df_num$Gender=as.numeric(df_num$Gender)

#0 = No, 1 = Yes
df_num$OverTime <- mapvalues(df_num$OverTime, from=c('Yes', 'No'), to = c(1,0))
df_num$OverTime=as.numeric(df_num$OverTime)

head(df_num)
```
## Exploratory Data Analaysis 
## Frequency of Categorical Levels
```{r}
df_cat = inspect_cat(df)
show_plot(df_cat)
```
## Employee Attrition 
For Attrition, 84% of the employees had "No" Attrition and 16% had "Yes" Attrition. 

```{r}
library(ggplot2)
#install.packages("cowplot")
library(cowplot)
attritions_number <- df_raw %>% group_by(Attrition) %>% dplyr::summarise(Count=n()) %>% ggplot(aes(x=Attrition, y=Count)) + geom_bar(stat="identity", fill="orange", color="grey40") + theme_bw() + coord_flip() + geom_text(aes(x=Attrition, y=0.01, label= Count), hjust=-0.8, vjust=-1, size=3,  colour="black", fontface="bold", angle=360) + labs(title="Employee Attrition (Amount)", x="Employee Attrition",y="Amount") + scale_fill_few(palette = 'Dark')+ theme_few()

attrition_percentage <- df %>% group_by(Attrition) %>% dplyr::summarise(Count=n()) %>% 
mutate(pct=round(prop.table(Count),2) * 100) %>% 
ggplot(aes(x=Attrition, y=pct)) + geom_bar(stat="identity", fill = "dodgerblue", color="grey40") + 
geom_text(aes(x=Attrition, y=0.01, label= sprintf("%.2f%%", pct)),
            hjust=0.5, vjust=-3, size=4, 
            colour="black", fontface="bold") + theme_bw() + labs(x="Employee Attrition", y="Percentage") + 
labs(title="Employee Attrition (%)") + scale_fill_few(palette = 'Dark')+ theme_few()



plot_grid(attritions_number, attrition_percentage, align="h", ncol=2)
```

## Age & Attrition 
```{r}
ggplot(df, aes(x = Age, fill = Attrition)) + geom_histogram(color="black")+
  labs(title="Age vs.Attirition",x="Attrition", y = "Monthly Income $")+ scale_fill_few(palette = 'Dark')+ theme_few()
```

## Monthly Income & Attrition
```{r}
# MonthlyIncome
ggplot(df, aes(x=Attrition, y=MonthlyIncome, color=Attrition, fill= Attrition)) +
  geom_boxplot( color = "black")+
  labs(title="Monthly Income vs. Attrition",x="Attrition", y = "Monthly Income $")+ scale_fill_few(palette = 'Dark')+ theme_few()
```
## Job Involvement & Attrition 
```{r}
library(ggthemes)
df %>% ggplot(aes(x = JobInvolvement, fill = Attrition)) +
  geom_bar(position = 'fill', color="black") +
  coord_flip() + 
  scale_fill_few(palette = 'Dark')+ theme_few() +ggtitle("Job Involvement & Attrition")
```

### Job Involvement & Attrition based on OverTime
```{r}
df %>% ggplot(aes(x = JobInvolvement, fill = Attrition)) +
  geom_bar(position = 'fill', color="black") +
  coord_flip() +
  facet_wrap( ~ OverTime) + 
  scale_fill_few(palette = 'Dark') + 
  theme_few() + ggtitle("Job Involvement & Attrition based on OverTime")
```

## Work-Life Balance & Attrition 
```{r}
df %>% ggplot(aes(x = WorkLifeBalance, fill = Attrition)) +
  geom_bar(position = 'fill', color="black") +
  coord_flip() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few() + ggtitle("Work-Life Balance & Attrition")
```
### Work-Life Balance & Attrition based on JobRole
```{r}
df %>% ggplot(aes(x = WorkLifeBalance, fill = Attrition)) +
  geom_bar(position = 'fill', color="black") +
  coord_flip() +
  facet_wrap( ~ JobRole) + 
  scale_fill_few(palette = 'Dark') + 
  theme_few() +ggtitle("Work-Life Balance & Attrition based on JobRole")
```
### Work-Life Balance & Attrition based on JobLevel 
```{r}
df %>% ggplot(aes(x = WorkLifeBalance, fill = Attrition)) +
  geom_bar(position = 'fill', color="black") +
  coord_flip() +
  facet_wrap( ~ JobLevel) + 
  scale_fill_few(palette = 'Dark') + 
  theme_few() +ggtitle("Work-Life Balance & Attrition based on JobLevel")
```
### Work-Life Balance & Attrition based on OverTime
```{r}
df %>% ggplot(aes(x = WorkLifeBalance, fill = Attrition)) +
  geom_bar(position = 'fill', color="black") +
  coord_flip() +
  facet_wrap( ~ OverTime) + 
  scale_fill_few(palette = 'Dark') + 
  theme_few() +ggtitle("Work-Life Balance & Attrition based on OverTime")
```
## OverTime & Attrition 
```{r}
df %>% ggplot(aes(x = OverTime, fill = Attrition)) +
  geom_bar(position = 'fill', color = "black") +
  coord_flip() + 
  scale_fill_few(palette = 'Dark') + 
  theme_few() +ggtitle("Overtime & Attrition")
```



## Correlation Plots
```{r}
library(corrplot)

corrplot(df_corr, method = "number",
           type = "upper",
           tl.cex = 0.7,
           tl.srt = 80,
           tl.col = "black")

corrplot(M, method="circle", type="upper")

head(df_corr)
df_corr$levels
```
- JobLevel highly correlated with MonthlyIncome & TotalWorkingYears
- Age & TotalWorkingYears highly correlated 
- YearsAtCompany highly correlated with YearsInCurrentRole & YearsSinceLastPromotion & YearsWithCurrManager

##  Feature Selection 
```{r}
library(caret)
# Feature Selection
# We need to find features which are important for the model.


# prepare training scheme
control <- trainControl(method="repeatedcv", number=10, repeats=3)
# train the model
model <- train(Attrition~., data=df, method="lvq", preProcess="scale", trControl=control)
# estimate variable importance
importance <- varImp(model, scale=FALSE)
# summarize importance
print(importance)
# plot importance
plot(importance)
```
- look at relationship between TotalWorkingYears + YearsAtCompany 
- YearsInCurrentRoleYearsWithCurrManager

### Ranked Cross-Validations 
Here we look at the top 10  most relevant correlations between variables. 
```{r}
devtools::install_github("laresbernardo/lares")
library(lares)

corr_cross(df , # name of dataset
  max_pvalue = 0.05, # display only significant correlations (at 5% level)
  top = 10 # display top 10 couples of variables (by correlation coefficient)
)
```
### Top Correlated Variables for Attrition & MonthlyIncome
```{r}
corr_var(df, Attrition, top=10)
corr_var(df, MonthlyIncome, top=10)
```

## MonthlyIncome Relationships 
```{r}
head(df_num)
```


# Models 
### Train/Test Split
```{r}
trainIndices = sample(seq(1:length(df$Age)),round(.7*length(df$Age)))
train = df[trainIndices,]
test = df[-trainIndices,]


head(train)
head(test)
dim(train) 
```

```{r}
# remove highly correlated variables 
vars_use = subset(df, select = -c(YearsWithCurrManager, YearsInCurrentRole, MonthlyRate, HourlyRate , DailyRate )) 
vars_use
```

## Linear Regression 




## Linear Model for MonthlyIncome 
### Model 1: Monthly Income & Job Level 
```{r}
#install.packages("Metrics")
library(Metrics)
fit_salary1 = lm(MonthlyIncome~JobLevel, data=train)
summary(fit_salary1)

preds_salary = predict(fit_salary1, test, interval="predict") 
rmse(train$MonthlyIncome, preds_salary)

plot(fit_salary1$residuals)

 

```

### Model 2: MonthlyIncome & JobLevel + TotalWorkingYears + JobRole

```{r}

fit_salary2 = lm(MonthlyIncome~JobLevel+TotalWorkingYears+JobRole+, data=train)
summary(fit_salary2)
sqrt(mean(fit_salary2$residuals^2)) #RMSE

preds_salary2 = predict(fit_salary2, test, interval="predict") 
#rmse(train$MonthlyIncome, preds_salary)
plot(fit_salary2)
```


```{r}
set.seed(1)
splitPerc = .7
iterations = 500
masterRMSE = matrix(nrow = iterations, 1)

  
for(j in 1:iterations)
{
  trainIndices = sample(1:dim(df_lm)[1],round(splitPerc * nrow(df_lm)))
  trainData = df_lm[trainIndices,]
  testData = df_lm[-trainIndices,]


  # linear model (after trying many combinations and ruling out variables that failed to improve RMSE and/or had high P values)
  linearMod <- lm(trainData$MonthlyIncome~JobLevel+TotalWorkingYears+JobRole, data=trainData)
  # 
  summary(linearMod)
  # now use it to predict the salary
  
  
  pred = predict(linearMod, testData, inverval="predict")
  
  masterRMSE[j,1] = rmse(testData$MonthlyIncome, pred)
}

meanRMSE = colMeans(masterRMSE)
meanRMSE
```

## Linear Model for Attrition
```{r}
df_lm$Attrition = as.numeric(df_lm$Attrition)
```


```{r}

library(car)

# Linear regression model on all variables 
fit1 = lm(Attrition ~ OverTime , data=train_num)
summary(fit1)
sqrt(mean(fit1$residuals^2)) #RMSE
#vif(fit1)
preds1 = predict(fit1, test_num, interval="predict") 
preds1
rmse(train_num$Attrition, preds1)

hist(fit1$residuals, col = "blue", main = "Histogram of Residuals")
plot(fit1$fitted.values,fit1$residuals, main = "Plot of Residuals v. Fitted Values")


 # Linear regression model on all variables 
fit2 = lm(Attrition ~ ., data=df_lm)
summary(fit2)
vif(fit2)
hist(fit2$residuals, col = "blue", main = "Histogram of Residuals")
plot(fit2$fitted.values,fit2$residuals, main = "Plot of Residuals v. Fitted Values")
sqrt(mean(fit2$residuals^2)) #RMSE

 # Linear regression model on all variables 
fit3 = lm(Attrition ~ OverTime + StockOptionLevel + MaritalStatus + JobSatisfaction + JobLevel + MonthlyIncome , data=df_lm)
summary(fit3)
vif(fit2)
hist(fit2$residuals, col = "blue", main = "Histogram of Residuals")
plot(fit2$fitted.values,fit2$residuals, main = "Plot of Residuals v. Fitted Values")
sqrt(mean(fit3$residuals^2)) #RMSE

```




```{r}

fit4 = lm(Attrition ~ BusinessTravel + Education + EnvironmentSatisfaction + JobLevel + JobRole + NumCompaniesWorked + WorkLifeBalance  + Age + DistanceFromHome + OverTime , data=df_lm)
summary(fit4)
vif(fit4)
hist(fit4$residuals, col = "blue", main = "Histogram of Residuals")
plot(fit4$fitted.values,fit2$residuals, main = "Plot of Residuals v. Fitted Values")
sqrt(mean(fit4$residuals^2)) #RMSE



```

```{r}
set.seed(1)
splitPerc = .7
iterations = 50
thresholdValues = seq(0,1,0.01)
thresholdIterations = length(thresholdValues)
masterAcc = matrix(nrow = iterations, ncol=thresholdIterations)
masterSpec = matrix(nrow = iterations, ncol=thresholdIterations)
masterSens = matrix(nrow = iterations, ncol=thresholdIterations)
masterCombined = matrix(nrow = iterations, ncol=thresholdIterations)


for(j in 1:iterations)
{
  
  trainIndices = sample(1:dim(df_num)[1],round(splitPerc * nrow(df_num)))
  trainData = df_num[trainIndices,]
  testData = df_num[-trainIndices,]
  

  fit <- lm(Attrition ~ BusinessTravel + Education + EnvironmentSatisfaction + JobLevel + JobRole + NumCompaniesWorked + WorkLifeBalance + JobRole + Age + DistanceFromHome + OverTime, data=trainData) 
  

  pred = predict(fit, testData, inverval="predict", type = "response")
  
  for (i in 1:length(thresholdValues))
  {
  
    pred <- ifelse(pred > thresholdValues[i], "Yes", "No")
  
    pred <- as.factor(pred)
  
    levels(pred) = levels(testData$Attrition)
    CM = confusionMatrix(table(pred, as.factor(testData$Attrition)),positive="Yes")
    masterAcc[j,i] = CM$overall[1]
    masterSens[j,i] = CM$byClass[1][[1]] # sensitivity
    masterSpec[j,i] = CM$byClass[2][[1]] # specificity
    masterCombined[j,i] =  CM$byClass[1][[1]] + CM$byClass[2][[1]] # combined
  }
}
# all the rows in the same column have the same threshold value, so average across the column to get the average for threshold
MeanAcc = colMeans(masterAcc)

plot(seq(1,thresholdIterations,1),MeanAcc, type = "l", xlab = "Threshold", ylab="Accuracy")

```





## KNN 

```{r}
# Using all variables
noAttrition_df = df[df$Attrition == 'No',]
yesAttrition_df= df[df$Attrition == 'Yes',]

trainingPercent = nrow(yesAttrition_df) / nrow(noAttrition_df)

trainingIndicies = sample(1:dim(noAttrition_df)[1], round(trainingPercent * dim(noAttrition_df)[1]))
train = rbind(noAttrition_df[trainingIndicies,], yesAttrition_df)
       
head(train)
#head(test)
#Train Control ... Repeated 10 fold CV
ctrl <- trainControl(method="repeatedcv")

knn_model1 <-train(Attrition ~ .,data=train, method="knn", trControl = ctrl, preProcess = c("center","scale"), tuneLength = 20)

knn_pred1 = predict(knn_model1, df)
CM= confusionMatrix(table(knn_pred1, df$Attrition), positive = "Yes")
CM

```
```{r}
# Using all variables
noAttrition_df = df[df$Attrition == 'No',]
yesAttrition_df= df[df$Attrition == 'Yes',]

trainingPercent = nrow(yesAttrition_df) / nrow(noAttrition_df)

trainingIndicies = sample(1:dim(noAttrition_df)[1], round(trainingPercent * dim(noAttrition_df)[1]))
train = rbind(noAttrition_df[trainingIndicies,], yesAttrition_df)
       
head(train)
#head(test)
#Train Control ... Repeated 10 fold CV
ctrl <- trainControl(method="repeatedcv")

knn_model2 <-train(Attrition ~ OverTime+EnvironmentSatisfaction+NumCompaniesWorked+Age+JobInvolvement+MonthlyIncome+MaritalStatus+StockOptionLevel,data=train, method="knn", trControl = ctrl, preProcess = c("center","scale"), tuneLength = 20)

knn_pred2 = predict(knn_model2, df)
CM= confusionMatrix(table(knn_pred2, df$Attrition), positive = "Yes")
CM

```


```{r}

noAttrition_df = df[df$Attrition == 'No',]
yesAttrition_df= df[df$Attrition == 'Yes',]

trainingPercent = nrow(yesAttrition_df) / nrow(noAttrition_df)

trainingIndicies = sample(1:dim(noAttrition_df)[1], round(trainingPercent * dim(noAttrition_df)[1]))
train_knn = rbind(noAttrition_df[trainingIndicies,], yesAttrition_df)
       

# validate train and test sets
head(train_knn)

# control settings for KNN
# NOTE: needed in order to focus on specificity

traincontrol_knn = trainControl(
  method = "repeatedcv",
  number = 5,
  repeats = 25,
  summaryFunction = twoClassSummary,
  classProbs = TRUE
)

# KNN on Training Set

knn_model <- train(Attrition ~ ., data = train_knn, method = "knn", metric = "Spec",  trControl = traincontrol_knn,  
                       preProcess = c("center","scale"), tuneLength = 20)

#Test
# Adding predictions to Test Data
knn_pred = predict(knn_model,newdata = test )

CM= confusionMatrix(table(knn_pred, test$Attrition), positive = "Yes")
CM
```

```{r}
# predictions for whole data set 
knn_pred = predict(knn_model, df)
CM= confusionMatrix(table(knn_pred, df$Attrition), positive = "Yes")
CM
```

##  NAIVE BAYES




```{r}
library(class)

trainingPercent = nrow(yesAttrition_df) / nrow(noAttrition_df)

trainingIndicies = sample(1:dim(noAttrition_df)[1], round(trainingPercent * dim(noAttrition_df)[1]))
train_nb = rbind(noAttrition_df[trainingIndicies,], yesAttrition_df)

nb_model1 = naiveBayes(Attrition~BusinessTravel + EnvironmentSatisfaction + JobLevel + JobRole + NumCompaniesWorked + WorkLifeBalance + JobRole + Age + DistanceFromHome + OverTime , data = train_nb)
summary(nb_model)
#table(nb,test$Age)
nb_pred1 = predict(nb_model, df)
CM= confusionMatrix(table(nb_pred1, df$Attrition), positive = "Yes")
CM
#cor(df$JobInvolvement, df$EnvironmentSatisfaction)
```

```{r}
nb_model2= naiveBayes(Attrition~BusinessTravel + EnvironmentSatisfaction + JobLevel + JobRole + NumCompaniesWorked + WorkLifeBalance + JobRole + Age + DistanceFromHome + OverTime,data = train_nb)
summary(nb_model2)

nb_pred2 = predict(nb_model2, df)
CM= confusionMatrix(table(nb_pred2, df$Attrition), positive = "Yes")
CM
```

```{r}
set.seed(1)
splitPerc = .7
iterations = 50
masterAcc = matrix(nrow = iterations, ncol = 1)
masterSpec = matrix(nrow = iterations, ncol = 1)
masterSens = matrix(nrow = iterations, ncol = 1)
  
for(j in 1:iterations)
{
  trainIndices = sample(1:dim(train)[1],round(splitPerc * nrow(train)))
  trainData = train[trainIndices,]
  testData = train[-trainIndices,]
  modelBayes = naiveBayes(Attrition~BusinessTravel + EnvironmentSatisfaction + JobLevel + JobRole + NumCompaniesWorked + WorkLifeBalance + JobRole + Age + DistanceFromHome + OverTime,data = trainData)
  predictAttrBayes = predict(modelBayes, testData)
  CM = confusionMatrix(table(predictAttrBayes, as.factor(testData$Attrition)),positive="Yes")
  
  masterAcc[j,1] = CM$overall[1]
  masterSens[j,1] = CM$byClass[1][[1]] # sensitivity
  masterSpec[j,1] = CM$byClass[2][[1]] # specificity
}
MeanAcc = colMeans(masterAcc)
MeanAcc
MeanSens = colMeans(masterSens)
MeanSens
MeanSpec = colMeans(masterSpec)
MeanSpec
CM

predictAttrBayes = predict(modelBayes, df)
CM = confusionMatrix(table(predictAttrBayes, as.factor(df$Attrition)),positive="Yes")
CM

```

## Validation Requirement for Salary 
```{r}
fit_salary_val = lm(MonthlyIncome~JobLevel+TotalWorkingYears+JobRole, data=df)
pred_salary_val = predict(fit_salary_val, df_salary)
summary(fit_salary_val)

MonthlyIncome = pred_salary_val 
MonthlyIncome = as.data.frame(MonthlyIncome)
salary_pred = cbind(df_salary, MonthlyIncome)

write.csv(salary_pred, "CarolinaCrausCase2PredictionsSalary.csv", row.names = FALSE)
case2nosalary3 <- read.csv("CarolinaCrausCase2PredictionsSalary.csv", header = T)
head(case2nosalary3)


```

